How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-16 tse-paper/content.tex
corrections study results and graphs
closes #39, closes #42

\section{Results}
This section presents the separate results for each chunk retrieval
technique.
We start with CTS, KWS and RLR, as their results are easiest to
understand.
Afterwards we compare the three techniques with each other and RLR as
baseline.

@@

\subsection{Common Text Similarity (CTS)}
\label{sec:r:cts}
\begin{figure*}
\centering
    \textbf{Common Text Similarity (CTS)}\par\medskip
\begin{subfigure}[t]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
		\caption{training set size.}
		\label{fig:recall-precision-examplecount-CTS}

\end{subfigure}\hspace{\fill}
\begin{subfigure}[t]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
		\caption{structural category count
		in training and test set.}
		\label{fig:recall-precision-categorycount-CTS}
\end{subfigure}
\caption{Precision, recall and F$_{1}$-score of chunk
retrieval with Common Text Similarity (CTS) compared by \ldots}
\end{figure*}

@@

\Cref{fig:recall-precision-categorycount-CTS} shows the same
measurements for an increasing number of structural categories in the
training and test examples.
With increasing category count, precision,
recall and F$_{1}$-score decrease.
Especially for more than three
categories present we have no chunk retrieval runs where all desired
lines were extracted.

@@

\Cref{fig:recall-precision-categorycount-KWS} shows the same
measurements for an increasing number of structural categories in the
training and test examples.
For more than one structural category in
the training and test examples the recall decreases by about 20\% and
the precision decreases about 6\%.
For more than two structural
categories no clear trend is visible in precision, recall or
F$_{1}$-score for an increasing amount of categories in the training
and test examples.

@@

In our evaluation, we compare against a baseline of randomly
picking lines from the build log.
Its results follow intuitive
expectations:
The precision ranges between 8\% and 5\%, the recall between 6\% and
8\%.
The size of the training set has no visible impact on either.
An larger number of structural categories within the training and
test sets decreased the precision of RLR from 7\% to 0\%, the recall
increases from 6\%, for one structural category present, to 11\%, for
three sturctural categories present and also drops to 0\% for more
structural categories.
Graphs of the results of the chunk retrieval with RLR from our study
are included in our replication
package~\cite{brandt2020chunk-replication}.

\subsection{Program Synthesis by Example (PBE)}
\label{sec:r:pbe}
\begin{figure*}
\centering
    \textbf{Program Synthesis by Example (PBE)}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
				\caption{Precision, recall and
				F$_{1}$-score when PBE could synthesize
				a consistent program compared with the
				size of the training set.}
		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
				\caption{Successfulness of retrieval
				compared by structural category count
				in training and test sets.}
		\label{fig:failure-reason-categorycount-PBE}
\end{subfigure}
\caption{Results of chunk retrieval with  Program Synthesis by Example
(PBE)}
\end{figure*}

\begin{figure}[tbp]
		\centering
		\includegraphics[width=0.75\columnwidth,
		clip]{img/big-study/failure-reason-pbe.pdf}
		\caption{Results of chunk retrieval with PBE.}
		\label{fig:failure-reason-PBE}
\end{figure}

\Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our
evaluation.
Out of the 400 runs, 5 per each one of the 80 example
sets, PBE extracted all the desired lines in 138 cases.
In 89 further
cases, an extraction program was also successfully synthesized, though
in 59 of the 89 cases the synthesized program yielded no output.
In 30
of the 89 cases did the synthesized program only partially extract a
subset of the desired lines.
For these 30 cases, the average recall
was 28\%.
\Cref{lst:pbe-unsuccessful} shows an example of such
an \emph{unsuccessful retrieval}, where the synthesized program only
retrieved two of the four targeted lines.
In 173 of the 400 cases
could PROSE not synthesize program consistent with all of the training
examples.

\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE
runs depend on the number of structural categories in the training and
test examples.
The figure demonstrates that program synthesis mostly
returns exactly the desired output when there are is only one
structural category present in the training examples.
However, when
two or more structural categories are simultaneously present in the
examlpe set, PROSE could in most cases not synthesize a program
consistent with all training examples.
For four or more present
categories PROSE could never synthesize a consistent program.

@@

\Cref{fig:success-partial-all} compares the success of chunk
retrievals differentiated by techniques in our study.
CTS and KWS
extract some of the desired lines in 79\% and 88.5\% of the chunk
retrieval runs.
With 38.25\%, KWS also has the highest number of fully
successful extractions, followed by PBE with 34.5\%.
PBE has the
lowest number of partial retrievals with only 18 out of 400 chunk
retrieval runs.

@@

\begin{figure*}
\centering
    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/big-study/recall-precision-singlecategory-all.pdf}
		\caption{Training and test examples in \emph{one}
		structural category.}
		\label{fig:recall-precision-singlecategory-all}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
				\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-multicategory-all.pdf}
		\caption{Training and test examples in $>1$ structural
		category.}
		\label{fig:recall-precision-multicategory-all}
\end{subfigure}
\caption{Precision, recall and F$_{1}$-score of all
techniques compared, split by structural category count.}
\end{figure*}

>>>>

\section{Results}
This section presents the separate results for each chunk retrieval
technique.
Afterwards we compare the three techniques with each other and RLR as
baseline.

\subsection{Program Synthesis by Example (PBE)}
\label{sec:r:pbe}

\begin{figure}[tbp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/failure-reason-pbe.pdf}
		\caption{Results of chunk retrieval with PBE.}
		\label{fig:failure-reason-PBE}
\end{figure}

@@

\begin{figure*}
\centering
    \textbf{Program Synthesis by Example (PBE)}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
				\caption{Successfulness of retrieval
				compared by structural category count
				in training and test sets.}
		\label{fig:failure-reason-categorycount-PBE}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
				\caption{Precision, recall and
				F$_{1}$-score when PBE could synthesize
				a consistent program compared with the
				size of the training set.}
		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
\end{subfigure}
\caption{Results of chunk retrieval with  Program Synthesis by Example
(PBE)}
\end{figure*}

\Cref{fig:failure-reason-PBE} presents the results of the chunk
retrieval with PBE.
Out of the 400 runs, 5 per each one of the 80 example
sets, PBE extracted all the desired lines successfully in 138 cases.
In 59 cases, a regular expression program could be synthesized, though
it did not find a match on the test build log.
In 30 cases the synthesized program only extracted a
subset of the desired lines.
For these 30 cases, the average recall
was 28\%.
\Cref{lst:pbe-unsuccessful} shows how an example of such
an \emph{unsuccessful retrieval}, where the synthesized program only
retrieved two of the four targeted lines.
In 173 of the 400 cases
could PROSE not synthesize program consistent with all of the training
examples.

\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE
runs depend on the number of structural categories in the training and
test examples.
The figure demonstrates that program synthesis mostly
returns exactly the desired output when there are is only one
structural category present in the training and test examples.
However, when
two or more structural categories are simultaneously present,
PROSE could in most cases not synthesize a program.
For four or more present
categories PROSE could never synthesize a consistent program.

\subsection{Common Text Similarity (CTS)}
\label{sec:r:cts}
\begin{figure*}
\centering
    \textbf{Common Text Similarity (CTS)}\par\medskip
\begin{subfigure}[tb]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
		\caption{training set size.}
		\label{fig:recall-precision-examplecount-CTS}

\end{subfigure}\hspace{\fill}
\begin{subfigure}[tb]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
		\caption{structural category count
		in training and test set.}
		\label{fig:recall-precision-categorycount-CTS}
\end{subfigure}
\caption{Precision, recall and F$_{1}$-score of chunk
retrieval with Common Text Similarity (CTS) compared by \ldots}
\end{figure*}

@@

\Cref{fig:recall-precision-categorycount-CTS} shows the same
measurements for an increasing number of structural categories in the
training and test examples.
With increasing category count, precision,
recall and F$_{1}$-score decrease.
% Especially for more than four
% categories present we have no chunk retrieval runs where all desired
% lines were extracted.

@@

\Cref{fig:recall-precision-categorycount-KWS} shows the same
measurements for an increasing number of structural categories in the
training and test examples.
For more than one structural category in
the training and test examples the recall decreases by about 20\% and
the precision decreases about 6\%.
For more than two structural
categories no clear trend is visible in precision, recall or
F$_{1}$-score.

@@

In our evaluation, we compare against a baseline of randomly
picking lines from the build log.
Its results follow intuitive
expectations:
The precision ranges between 8\% and 5\%, the recall between 6\% and
8\%.
The size of the training set has no visible impact on either.
An larger number of structural categories within the training and
test sets decreased the precision of RLR from 7\% to 0\%, the recall
increases from 6\%, for one structural category present, to 11\%, for
three structural categories present and also drops to 0\% for more
structural categories.
Graphs of these results of the chunk retrieval with RLR
are included in our replication
package~\cite{brandt2020chunk-replication}.

@@

\Cref{fig:success-partial-all} compares the success of chunk
retrievals differentiated by techniques in our study.
CTS and KWS
extract at least some of the desired lines in 79\% and 88.5\%
of the chunk retrieval runs.
With 38.25\%, KWS also has the highest proportion of fully
successful extractions, followed by PBE with 34.5\%.
PBE has the
lowest number of partial retrievals with only 18 out of 400 chunk
retrieval runs.

@@

\begin{figure*}
\centering
    \textbf{PBE, CTS, KWS, and RLR}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/big-study/recall-precision-singlecategory-all.pdf}
		\caption{Training and test examples in 1
		structural category.}
		\label{fig:recall-precision-singlecategory-all}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
				\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-multicategory-all.pdf}
		\caption{Training and test examples in \textgreater
		1 structural
		category.}
		\label{fig:recall-precision-multicategory-all}
\end{subfigure}
\caption{Precision, recall and F$_{1}$-score of all
techniques compared, split by structural category count.}
\end{figure*}
